## 10 tourist attractions in Argentina

Author: Maximiliano

Date: 10/11/2020

### Overview

The objective of this project is to create a web page using R Markdown that features a map created with Leaflet. We will display in the map 10 tourist attractions in Argentina.

### Creating the map

Loading Leaflet library

```{r, warning=FALSE, message=FALSE}
library(leaflet)
```

Creating the data

```{r}
touristAttractionsArgCoordinates <- data.frame(
        lat=c(-50,-32.653197,-25.686667,-42.8075,-49.271278,-41,-35.1476,
              -29.8,-40.833333,-23.7469),
        lng=c(-73.249444,-70.0112,-54.444722,-71.898889,-73.043222,-71.5,
              -70.0828,-67.833333,-71.616667,-65.5035))
touristAttractionsArgNames <- c("Los Glaciares National Park",
                                "Aconcagua mountain","Iguazu Falls", 
                                "Los Alerces National Park","Fitz Roy mountain"
                                ,"Nahuel Huapi National Park", "Las Leñas",
                                "Talampaya National Park",
                                "Los Arrayanes National Park",
                                "Cerro de los 7 colores")
```

Creating the icon

```{r}
ArgIcon <- makeIcon(
        iconUrl = "https://www.casarosada.gob.ar/images/1024px-Escarapela_argentina.svg.png",
        iconWidth = 30, iconHeight = 30, iconAnchorX = 15, iconAnchorY = 15)
```

Creating the map

```{r}
touristAttractionsArgMap <- touristAttractionsArgCoordinates %>%
        leaflet() %>% addTiles() %>% 
        addMarkers(popup = touristAttractionsArgNames,
                   clusterOptions = markerClusterOptions(),
                   icon = ArgIcon)
```        
        
Displaying the map

**Click the icons to see the names**
        
```{r}      
touristAttractionsArgMap    
```
    
        